---
title: "Disability atlas in Sub-Saharan Africa"
format:
  html: 
    grid:
      sidebar-width: 250px
      body-width: 1050px
      margin-width: 300px
date: today
lightbox: true
toc: true
code-fold: true
execute: 
  warning: false
  message: false
editor: visual
---

# Loading data

```{r}
#| include = TRUE 
# We include code chunks but there are folded

library(srvyr)
library(tidyverse)
library(gtsummary)
theme_gtsummary_language(language = "fr", decimal.mark = ",", big.mark = " ")
options(survey.lonely.psu = "adjust") # Added for the case where there may be a single PSU in a strata, as indicated here https://www.youtube.com/watch?v=pJwd2-m3QBY ; if we don't add this we get an error when we make the tbl_svysummary for saoto19wt
#Sys.setlocale("LC_ALL", "en_US.UTF-8")
#options(encoding = "UTF-8") 
# Two lines above to make sure the symbol ° (for long and lat) displays correctly in the maps, but doesn't make it
# In case it doesn't work https://stackoverflow.com/questions/75758155/the-longitude-and-latitude-coordinates-on-an-sf-ggplot-map-are-displaying-with-b
load("../data/data_atlas.RData") # this is built in 00_built.R and contains the datasets saved at the end of 02_recoding_dhs and at the end of 03_recoding_mics
list2env(dhs_recoded, envir = .GlobalEnv) # To unwrap the "list" dhs_recoded
list2env(mics_recoded, envir = .GlobalEnv) # Idem
library(rnaturalearth) # For the basemap of the african continent
```


# National prevalences of disability (at the smallest possible level)

## Tables for DHS countries

```{r}
make_prev_tb <- function(country99wt, smallest_admin) {
  country99wt |>
    tbl_svysummary(
      by = c({{smallest_admin}}), # bracket technique for quotes found here https://stackoverflow.com/questions/58926917/how-to-refer-to-the-function-arguments-in-quotes
      include = c("at_least_alotof_diff_any_domain", "at_least_alotof_diff_see", "at_least_alotof_diff_hear", "at_least_alotof_diff_com", "at_least_alotof_diff_remem", "at_least_alotof_diff_walk", "at_least_alotof_diff_wash"),
      type = list(
        #at_least_alotof_diff_any_domain ~ "categorical" # This displays the frequency for both "yes"/"no", rather than for just "no"
      ),
      statistic = ~"{p}% ({n_unweighted})",
      digits = ~ c(1, 0),
      label = list(
        variable = "Prevalence of variable"
      )
    ) |>
    modify_header(label ~ "**Variable**") |>
    modify_spanning_header(everything() ~ "**Prevalence (weighted)**")
}

# Note that the admin2 variables are the ones before the recoding when we merge the prevalence table to a basemap

make_prev_tb(kenya22wt, admin2) # TODO Change below the tables for MICS countries # Note 27/11: I can do it easily with "kenya22_prev_admin2 <- kenya22_prev_admin2 |> mutate(admin2 = NAME_2/strata/district/NAME_2)" at the end of the prevalence section for each country, but I'll wait until I'm a little more advanced to see if it's more useful or confusing
make_prev_tb(malawi16wt, admin2)
make_prev_tb(mali18wt, admin2)
make_prev_tb(maurit19wt, admin2)
make_prev_tb(mozam22wt, admin2)
make_prev_tb(nigeria18wt, admin3)
make_prev_tb(rwanda19wt, admin2)
make_prev_tb(senegal18wt, admin2)
make_prev_tb(senegal19wt, admin2)
make_prev_tb(safrica16wt, admin2)
make_prev_tb(tanza22wt, admin2)
make_prev_tb(uganda16wt, admin2)
```

## Tables for MICS countries

```{r}

make_prev_tb(benin21wt, admin1)
make_prev_tb(centraf18wt, admin1)
make_prev_tb(chad19wt, admin1)
make_prev_tb(comor22wt, admin2)
make_prev_tb(drcong17wt, admin1)
make_prev_tb(eswat21wt, admin2)
make_prev_tb(gamb18wt, admin2)
make_prev_tb(ghana17wt, admin1)
make_prev_tb(guibi18wt, admin1)
make_prev_tb(lesot18wt, admin2)
make_prev_tb(madag18wt, admin2)
make_prev_tb(malawi19wt, admin3)
make_prev_tb(saoto19wt, admin2)
make_prev_tb(sierral17wt, admin3)
make_prev_tb(togo17wt, admin1)
#make_prev_tb(yemen22wt, admin1)
make_prev_tb(zimbab19wt, admin2)

```


# Maps of sub-national disability prevalence for vision disability, for each country

## DHS countries

### Kenya

#### Kenya, population aged 18-49 years old, by Counties
```{r}
ggplot(kenya22_prev_admin1) + geom_sf(aes(fill = see_prev))
```

#### Kenya, population aged 18-49 years old, by Sub-counties
```{r}
ggplot(kenya22_prev_admin2) + geom_sf(aes(fill = see_prev))
```


### Malawi DHS
In this survey the disability questions are asked only to children 10-17 years old and not to adults.

#### Malawi DHS, population aged 10-17 years old, by Regions
```{r}
ggplot(malawi16_prev_admin1) + geom_sf(aes(fill = see_prev)) 
```

#### Malawi DHS, population aged 10-17 years old, by Districts
```{r}
ggplot(malawi16_prev_admin2) + geom_sf(aes(fill = see_prev))
```


### Mali

#### Mali, population aged 18-49 years old, by Regions
```{r}
ggplot(mali18_prev_admin1) + geom_sf(aes(fill = see_prev))
```

#### Mali, population aged 18-49 years old, by Cercles
```{r}
ggplot(mali18_prev_admin2) + geom_sf(aes(fill = see_prev))
```


### Mauritania

#### Mauritania, population aged 18-49 years old, by Regions (Wilayat)
```{r}
ggplot(maurit19_prev_admin1) + geom_sf(aes(fill = see_prev)) + labs(caption = "The regions Tiris Zemmour and Inchiri of Mauritania were grouped into \n1 region in the MICS survey (which means that \nthey have the same prevalence value)")
```

#### Mauritania, population aged 18-49 years old, by Departments (Moughataas)
```{r}
ggplot(maurit19_prev_admin2) + geom_sf(aes(fill = see_prev))
```


### Mozambique

#### Mozambique, population aged 18-49 years old, by Provinces
```{r}
ggplot(mozam22_prev_admin1) + geom_sf(aes(fill = see_prev))
```

#### Mozambique, population aged 18-49 years old, by Districts
```{r}
ggplot(mozam22_prev_admin2) + geom_sf(aes(fill = see_prev))
```


### Nigeria

#### Nigeria, population aged 18-49 years old, by Geopolitical zones
```{r}
ggplot(nigeria18_prev_admin1) + geom_sf(aes(fill = see_prev))
```

#### Nigeria, population aged 18-49 years old, by States
```{r}
ggplot(nigeria18_prev_admin2) + geom_sf(aes(fill = see_prev))
```

#### Nigeria, population aged 18-49 years old, by Local government areas
```{r}
ggplot(nigeria18_prev_admin3) + geom_sf(aes(fill = see_prev))
```


### Rwanda

#### Rwanda, population aged 18-49 years old, by Provinces (Intara)
```{r}
ggplot(rwanda19_prev_admin1) + geom_sf(aes(fill = see_prev))
```

#### Rwanda, population aged 18-49 years old, by Districts (Uturere)
```{r}
ggplot(rwanda19_prev_admin2) + geom_sf(aes(fill = see_prev))
```


### Senegal 2018

#### Senegal 2018, population aged 18-49 years old, by Regions
```{r}
ggplot(senegal18_prev_admin1) + geom_sf(aes(fill = see_prev))
```

#### Senegal 2018, population aged 18-49 years old, by Departments
```{r}
ggplot(senegal18_prev_admin2) + geom_sf(aes(fill = see_prev))
```


### Senegal 2019

#### Senegal 2019, population aged 18-49 years old, by Regions
```{r}
ggplot(senegal19_prev_admin1) + geom_sf(aes(fill = see_prev))
```

#### Senegal 2019, population aged 18-49 years old, by Departments
```{r}
ggplot(senegal19_prev_admin2) + geom_sf(aes(fill = see_prev))
```


### South Africa

#### South Africa, population aged 18-49 years old, by Provinces
```{r}
ggplot(safrica16_prev_admin1) + geom_sf(aes(fill = see_prev))
```

#### South Africa, population aged 18-49 years old, by Districts
```{r}
ggplot(safrica16_prev_admin2) + geom_sf(aes(fill = see_prev))
```


### Tanzania

#### Tanzania, population aged 18-49 years old, by Regions (Mikoa)
```{r}
ggplot(tanza22_prev_admin1) + geom_sf(aes(fill = see_prev))
```

#### Tanzania, population aged 18-49 years old, by Districts (Wilaya)
```{r}
ggplot(tanza22_prev_admin2) + geom_sf(aes(fill = see_prev))
```


### Uganda

#### Uganda, population aged 18-49 years old, by Sub-regions
```{r}
ggplot(uganda16_prev_admin1) + geom_sf(aes(fill = see_prev))
```

#### Uganda, population aged 18-49 years old, by Districts
```{r}
ggplot(uganda16_prev_admin2) + geom_sf(aes(fill = see_prev))
```

## MICS countries

### Benin

#### Benin, population aged 18-49 years old, by Departments
```{r}
ggplot(benin21_prev_admin1) + geom_sf(aes(fill = see_prev))
```


### Central African Republic

#### Central African Republic, population aged 18-49 years old, by Prefectures
```{r}
ggplot(centraf18_prev_admin1) + geom_sf(aes(fill = see_prev)) + labs(caption = "The 17 prefectures of Central African Republic were grouped into \n7 regions in the MICS survey (which means that prefectures \ngrouped in the same region have the same prevalence value)")
```


### Chad

#### Chad, population aged 18-49 years old, by Regions
```{r}
ggplot(chad19_prev_admin1) + geom_sf(aes(fill = see_prev))
```


### Comores

#### Comores, population aged 18-49 years old, by Islands
```{r}
ggplot(comor22_prev_admin1) + geom_sf(aes(fill = see_prev))
```

#### Comores, population aged 18-49 years old, by Prefectures
```{r}
ggplot(comor22_prev_admin2) + geom_sf(aes(fill = see_prev))
```


### Democratic Republic of the Congo

#### Democratic Republic of the Congo, population aged 18-49 years old, by Provinces
```{r}
ggplot(drcong17_prev_admin1) + geom_sf(aes(fill = see_prev))
```


### Eswatini

#### Eswatini, population aged 18-49 years old, by Regions
```{r}
ggplot(eswat21_prev_admin1) + geom_sf(aes(fill = see_prev))
```

#### Eswatini, population aged 18-49 years old, by constituencies (Tinkhundla)
```{r}
ggplot(eswat21_prev_admin2) + geom_sf(aes(fill = see_prev))
```


### Gambia

#### Gambia, population aged 18-49 years old, by Local government areas
```{r}
ggplot(gamb18_prev_admin1) + geom_sf(aes(fill = see_prev))
```

#### Gambia, population aged 18-49 years old, by Districts
```{r}
ggplot(gamb18_prev_admin2) + geom_sf(aes(fill = see_prev))
```


### Ghana

#### Ghana, population aged 18-49 years old, by Regions
```{r}
ggplot(ghana17_prev_admin1) + geom_sf(aes(fill = see_prev))
```


### Guinea-Bissau

#### Guinea-Bissau, population aged 18-49 years old, by Regions
```{r}
ggplot(guibi18_prev_admin1) + geom_sf(aes(fill = see_prev))
```


### Lesotho

#### Lesotho, population aged 18-49 years old, by Ecological regions
```{r}
ggplot(lesot18_prev_admin1) + geom_sf(aes(fill = see_prev))
```

#### Lesotho, population aged 18-49 years old, by Districts
```{r}
ggplot(lesot18_prev_admin2) + geom_sf(aes(fill = see_prev))
```


### Madagascar

#### Madagascar, population aged 18-49 years old, by Regions
```{r}
ggplot(madag18_prev_admin1) + geom_sf(aes(fill = see_prev))
```

#### Madagascar, population aged 18-49 years old, by Districts
```{r}
ggplot(madag18_prev_admin2) + geom_sf(aes(fill = see_prev))
```


### Malawi MICS

#### Malawi MICS, population aged 18-49 years old, by Regions
```{r}
ggplot(malawi19_prev_admin1) + geom_sf(aes(fill = see_prev))
```

#### Malawi MICS, population aged 18-49 years old, by Districts
```{r}
ggplot(malawi19_prev_admin2) + geom_sf(aes(fill = see_prev))
```

#### Malawi MICS, population aged 18-49 years old, by Traditional authorities
```{r}
ggplot(malawi19_prev_admin3) + geom_sf(aes(fill = see_prev))
```


### São Tomé and Príncipe

#### São Tomé and Príncipe, population aged 18-49 years old, by Provinces
```{r}
ggplot(saoto19_prev_admin1) + geom_sf(aes(fill = see_prev))
```

#### São Tomé and Príncipe, population aged 18-49 years old, by Districts
```{r}
ggplot(saoto19_prev_admin2) + geom_sf(aes(fill = see_prev)) + labs(caption = "The 7 districts of São Tomé and Príncipe were grouped into \n5 regions in the MICS survey (which means that districts \ngrouped in the same region have the same prevalence value)")
```


### Sierra Leone

#### Sierra Leone, population aged 18-49 years old, by Provinces
```{r}
ggplot(sierral17_prev_admin1) + geom_sf(aes(fill = see_prev))
```

#### Sierra Leone, population aged 18-49 years old, by Districts
```{r}
ggplot(sierral17_prev_admin2) + geom_sf(aes(fill = see_prev))
```

#### Sierra Leone, population aged 18-49 years old, by Chiefdoms
```{r}
ggplot(sierral17_prev_admin3) + geom_sf(aes(fill = see_prev))
```


### Togo

#### Togo, population aged 18-49 years old, by Regions
```{r}
ggplot(togo17_prev_admin1) + geom_sf(aes(fill = see_prev))
```


### Zimbabwe

#### Zimbabwe, population aged 18-49 years old, by Provinces
```{r}
ggplot(zimbab19_prev_admin1) + geom_sf(aes(fill = see_prev))
```

#### Zimbabwe, population aged 18-49 years old, by Districts
```{r}
ggplot(zimbab19_prev_admin2) + geom_sf(aes(fill = see_prev))
```


# Map of national disability prevalence for vision disability, for all available SSA countries

Note that for all maps showing the full African continent, the values shown for Senegal are from the 2019 DHS survey.

## National level for both DHS and MICS countries

```{r}
africa_map <- ne_countries(scale = "medium", returnclass = "sf", continent = "africa") # Example from: https://r-spatial.org/r/2018/10/25/ggplot2-sf.html, also here https://stackoverflow.com/questions/75177359/plotting-geographic-data-with-geom-sf

country_level_prevalences_dhs <- bind_rows(
  "Kenya" = kenya22_prev_admin0,
  "Malawi" = malawi16_prev_admin0,
  "Mali" = mali18_prev_admin0,
  "Mauritania" = maurit19_prev_admin0,
  "Mozambique" = mozam22_prev_admin0,
  "Nigeria" = nigeria18_prev_admin0,
  "Rwanda" = rwanda19_prev_admin0,
  "Senegal" = senegal19_prev_admin0,
  "South Africa" = safrica16_prev_admin0,
  "Tanzania" = tanza22_prev_admin0,
  "Uganda" = uganda16_prev_admin0,
  .id = "country_name"
  ) |> 
  mutate(origin_survey = "dhs") # We add a variable with the origin survey of the data

country_level_prevalences_mics <- bind_rows(
  "Benin" = benin21_prev_admin0,
  "Central African Rep." = centraf18_prev_admin0,
  "Chad" = chad19_prev_admin0,
  "Comoros" = comor22_prev_admin0,
  "Dem. Rep. Congo" = drcong17_prev_admin0,
  "eSwatini" = eswat21_prev_admin0,
  "Gambia" = gamb18_prev_admin0,
  "Ghana" = ghana17_prev_admin0,
  "Guinea-Bissau" = guibi18_prev_admin0,
  "Lesotho" = lesot18_prev_admin0,
  "Madagascar" = madag18_prev_admin0,
  "Malawi" = malawi19_prev_admin0,
  "São Tomé and Principe" = saoto19_prev_admin0,
  "Sierra Leone" = sierral17_prev_admin0,
  "Togo" = togo17_prev_admin0,
  "Zimbabwe" = zimbab19_prev_admin0,
  .id = "country_name"
  ) |> 
  mutate(origin_survey = "mics") # We add a variable with the origin survey of the data

country_level_prevalences <- country_level_prevalences_dhs |> 
  filter(country_name != "Malawi") |> # We keep malawi19 from MICS and not malawi16 from DHS
  bind_rows(country_level_prevalences_mics)

# To check that no countries from country_level_prevalences is excluded : anti_join(country_level_prevalences, africa_map, by = join_by(country_name == name))
africa_map <- left_join(africa_map, country_level_prevalences, by = join_by(name == country_name)) # We made sure above that in the table "country_level_prevalences", the name of the left was written similarly as the variable "name" in "africa_map"

ggplot(data = africa_map) +
  geom_sf(aes(fill = see_prev))
```
## National level for only DHS countries

```{r}
ggplot(data = africa_map |> mutate(see_prev = if_else(origin_survey == "dhs", see_prev, NA))) + # This removes the values in the see_prev variable for countries not from DHS
  geom_sf(aes(fill = see_prev))
```

## National level for only MICS countries

```{r}
ggplot(data = africa_map |> mutate(see_prev = if_else(origin_survey == "mics", see_prev, NA))) + # This removes the values in the see_prev variable for countries not from MICS
  geom_sf(aes(fill = see_prev))
```


# Map of sub-national disability prevalence for vision disability, for all available SSA countries

## Admin 1 level for both DHS and MICS countries

```{r}

admin1_level_prevalences_dhs <- bind_rows( # The homogeneization of the name of the admin 1 variable is not necessary, but the homogeneization of the geom variable is necessary for the map to be displayed correctly
  "Kenya" = kenya22_prev_admin1,
  "Malawi" = malawi16_prev_admin1,
  "Mali" = mali18_prev_admin1,
  "Mauritania" = maurit19_prev_admin1,
  "Mozambique" = mozam22_prev_admin1,
  "Nigeria" = nigeria18_prev_admin1,
  "Rwanda" = rwanda19_prev_admin1,
  "Senegal" = senegal19_prev_admin1,
  "South Africa" = safrica16_prev_admin1,
  "Tanzania" = tanza22_prev_admin1,
  "Uganda" = uganda16_prev_admin1,
  .id = "country_name"
) |> 
  mutate(origin_survey = "dhs") # We add a variable with the origin survey of the data

admin1_level_prevalences_mics <- bind_rows(
  "Benin" = benin21_prev_admin1,
  "Central African Rep." = centraf18_prev_admin1,
  "Chad" = chad19_prev_admin1,
  "Comoros" = comor22_prev_admin1,
  "Dem. Rep. Congo" = drcong17_prev_admin1,
  "eSwatini" = eswat21_prev_admin1,
  "Gambia" = gamb18_prev_admin1,
  "Ghana" = ghana17_prev_admin1,
  "Guinea-Bissau" = guibi18_prev_admin1,
  "Lesotho" = lesot18_prev_admin1,
  "Madagascar" = madag18_prev_admin1,
  "Malawi" = malawi19_prev_admin1,
  "São Tomé and Principe" = saoto19_prev_admin1,
  "Sierra Leone" = sierral17_prev_admin1,
  "Togo" = togo17_prev_admin1,
  "Zimbabwe" = zimbab19_prev_admin1,
  .id = "country_name"
) |> 
  mutate(origin_survey = "mics") # We add a variable with the origin survey of the data


admin1_level_prevalences <- admin1_level_prevalences_dhs |> 
  filter(country_name != "Malawi") |> # We keep malawi19 from MICS and not malawi16 from DHS
  bind_rows(admin1_level_prevalences_mics)

ggplot(data = africa_map) +
  geom_sf() +
  geom_sf(data = admin1_level_prevalences, aes(fill = see_prev))
```
## Admin 1 level for only DHS countries

```{r}
ggplot(data = africa_map) +
  geom_sf() +
  geom_sf(data = admin1_level_prevalences |> filter(origin_survey == "dhs"), aes(fill = see_prev)) # This filters out countries not from DHS
```

## Admin 1 level for only MICS countries

```{r}
ggplot(data = africa_map) +
  geom_sf() +
  geom_sf(data = admin1_level_prevalences |> filter(origin_survey == "mics"), aes(fill = see_prev)) # This filters out countries not from MICS
```

# Map of sub-national disability prevalence, at the smallest possible level, for vision disability, for all available SSA countries

## Smallest possible level for both DHS and MICS countries

```{r}

admin2_level_prevalences_dhs <- bind_rows(
  "Kenya" = kenya22_prev_admin2,
  "Malawi" = malawi16_prev_admin2,
  "Mali" = mali18_prev_admin2,
  "Mauritania" = maurit19_prev_admin2,
  "Mozambique" = mozam22_prev_admin2,
  "Nigeria" = nigeria18_prev_admin2,
  "Rwanda" = rwanda19_prev_admin2,
  "Senegal" = senegal19_prev_admin2,
  "South Africa" = safrica16_prev_admin2,
  "Tanzania" = tanza22_prev_admin2,
  "Uganda" = uganda16_prev_admin2,
  .id = "country_name"
) |> 
  mutate(origin_survey = "dhs") # We add a variable with the origin survey of the data

admin2_level_prevalences_mics <- bind_rows(
  "Comoros" = comor22_prev_admin2,
  "eSwatini" = eswat21_prev_admin2,
  "Gambia" = gamb18_prev_admin2,
  "Lesotho" = lesot18_prev_admin2,
  "Madagascar" = madag18_prev_admin2,
  "Malawi" = malawi19_prev_admin3,
  "São Tomé and Principe" = saoto19_prev_admin2,
  "Sierra Leone" = sierral17_prev_admin3,
  "Zimbabwe" = zimbab19_prev_admin2,
  .id = "country_name"
) |> 
  mutate(origin_survey = "mics") # We add a variable with the origin survey of the data

admin2_level_prevalences <- admin2_level_prevalences_dhs |> 
  filter(country_name != "Malawi") |> # We keep malawi19 from MICS and not malawi16 from DHS
  bind_rows(admin2_level_prevalences_mics)

ggplot(data = africa_map) +
  geom_sf() +
  geom_sf(data = admin2_level_prevalences, aes(fill = see_prev))

```

## Smallest possible level for only DHS countries

```{r}
ggplot(data = africa_map) +
  geom_sf() +
  geom_sf(data = admin2_level_prevalences |> filter(origin_survey == "dhs"), aes(fill = see_prev)) # This filters out countries not from DHS
```


## Smallest possible level for only MICS countries (only for the 9 MICS countries for which it was possible to go to a subdivision smaller than admin1)

```{r}
ggplot(data = africa_map) +
  geom_sf() +
  geom_sf(data = admin2_level_prevalences|> filter(origin_survey == "mics"), aes(fill = see_prev)) # This filters out countries not from MICS
```

